Ethnicity sensitive author disambiguation using semi-supervised learning

### 2016-01-18 paper/author_disambiguation.tex

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (\eg, the author name, his
affiliation, along with any other metadata that can be derived from $p$, as illustrated in Figure~\ref{fig:signature}). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$.

@@

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
or study.
Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \cite{scikitlearn} for the supervised learning
of a linkage function and of SciPy \cite{scipy} for clustering.
All components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \cite{scikitlearnAPI}, making them easy to maintain,
understand and reuse.
Our implementation is made to be efficient, exploiting parallelization when available, and ready for production environments.
It is also designed to be runnable
in an incremental fashion, by enabling disambiguation only on specified blocks if desired,
instead of having to run the disambiguation process on the whole signature set.

@@

\begin{table*}
\caption{Average precision, recall and B3 f-measure scores on test folds.}
\label{table:results}
\centering
\begin{tabular}{|l|c c c|}
  \hline
                       & \multicolumn{3}{|c|}{\textbf{B3}} \\
  \textbf{Description} & $P$ & $R$ & $F$ \\
  \hline
  \hline
Baseline & 0.9901 & 0.9760 & 0.9830  \\
\hline
Blocking = SFI & 0.9901 & 0.9760 & 0.9830  \\
Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841  \\
Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850} \\
Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 \\
\hline
No name normalization & 0.9887 & 0.9697 & 0.9791  \\
Name normalization & 0.9901 & 0.9760 & \textbf{0.9830}  \\
\hline
Classifier = GBRT & 0.9901 & 0.9760 & 0.9830  \\
Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846}  \\
Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666  \\
\hline
Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711  \\
Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786  \\
Training pairs = Blocked, balanced & 0.9901 & 0.9760 & \textbf{0.9830}  \\
\hline
Clustering = Average linkage & 0.9901 & 0.9760 & \textbf{0.9830}  \\
Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671  \\
Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785  \\
\hline
No cut & 0.9024 & 0.9828 & 0.9409  \\
Global cut & 0.9892 & 0.9737 & 0.9814  \\
Block cut & 0.9901 & 0.9760 & \textbf{0.9830}  \\
\hline
Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862}  \\
  \hline
\end{tabular}
\end{table*}

\begin{table*}
\caption{Average precision, recall and pairwise f-measure scores on test folds.}
\label{table:resultspw}
\centering
\begin{tabular}{|l|c c c|}
  \hline
                       & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
  \textbf{Description} & $P$ & $R$ & $F$\\
  \hline
  \hline
Baseline & 0.9948 & 0.9738 & 0.9842 \\
\hline
Blocking = SFI & 0.9948 & 0.9738 & 0.9842 \\
Blocking = Double metaphone & 0.9927 & 0.9817 & 0.9871 \\
Blocking = NYSIIS  & 0.9936 & 0.9814 & \textbf{0.9875} \\
Blocking = Soundex & 0.9935 & 0.9725 & 0.9828 \\
\hline
No name normalization & 0.9931 & 0.9658 & 0.9793 \\
Name normalization& 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Classifier = GBRT & 0.9948 & 0.9738 & 0.9842 \\
Classifier = Random Forests & 0.9957 & 0.9752 & \textbf{0.9854} \\
Classifier = Linear Regression & 0.9717 & 0.9569 & 0.9643 \\
\hline
Training pairs = Non-blocked, uniform & 0.9756 & 0.9629 & 0.9692 \\
Training pairs = Blocked, uniform & 0.9850 & 0.9707 & 0.9778 \\
Training pairs = Blocked, balanced  & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Clustering = Average linkage& 0.9948 & 0.9738 & \textbf{0.9842} \\
Clustering = Single linkage & 0.9543 & 0.9626 & 0.9584 \\
Clustering = Complete linkage & 0.9920 & 0.9688 & 0.9803 \\
\hline
No cut& 0.8298 & 0.9776 & 0.8977 \\
Global cut & 0.9940 & 0.9727 & 0.9832 \\
Block cut& 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Combined best settings & 0.9954 & 0.9805 & \textbf{0.9879} \\
  \hline
\end{tabular}
\end{table*}

\textit{Baseline.} Results presented in Table~\ref{table:results} are discussed with
respect to a baseline solution using the following combination of components:
\begin{itemize}
\item Blocking: same surname and the same first given name initial strategy (SFI);
\item Linkage function: all 22 features defined in Table~\ref{table:features},
    gradient boosted regression trees as supervised learning algorithm
    and a training set of pairs built from $({\cal S}_\text{train}^\prime, {\cal C}_\text{train}^\prime)$, by balancing easy and difficult cases.
\item Clustering: agglomerative clustering using average linkage and
    block cuts found to maximize $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
\end{itemize}

\textit{Blocking.} The good precision of the baseline ($0.9901$), but its
lower recall ($0.9760$) suggest that the blocking strategy might be the
limiting factor to further overall improvements.
As shown in Table~\ref{table:blocking}, the maximum recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
At the price of fewer and therefore slightly larger blocks (as reported in the right column of Table~\ref{table:blocking}), the
proposed phonetic-based blocking strategies show better maximum recall (all
around $0.9905$), thereby pushing further the upper bound on the maximum
performance of author disambiguation.
Let us remind however that the reported maximum recalls for the blocking strategies using phonetization are
also raised due to the better handling of multiple surnames, as described in Section \ref{methods:blocking}.

As Table~\ref{table:results} shows, switching to either Double metaphone or NYSIIS phonetic-based blocking allows
to improve the overall F-measure score, trading precision for recall.
In particular, the NYSIIS-based phonetic blocking shows to be the most effective when applied
to the baseline (with an F-measure of $0.9850$) while also being the most
efficient computationally (with 10857 blocks versus 12978 for the baseline).

@@

\textit{Name normalization.} As discussed previously, the seemingly insignificant step of
normalizing author names (stripping accents, removing affixes), as performed in the
baseline, is shown to be important. Results from Table~\ref{table:results} clearly suggest that not
normalizing significantly reduces performance (yielding an F-measure of $0.9830$ when normalizing,
but decreasing to $0.9791$ when raw author name strings are used instead).

\textit{Linkage function.} Let us first comment on the results regarding the
supervised algorithm used to learn the linkage function.
As Table~\ref{table:results} indicates, both tree-based algorithms appear to be
significantly better fit than Linear Regression ($0.9830$ and $0.9846$ for GBRT
and Random Forests versus $0.9666$ for Linear Regression). This result is
consistent with \cite{treeratpituk2009disambiguating} which evaluated the use of
Random Forests for author disambiguation, but contradicts results of
\cite{levin2012citation} for which Logistic Regression appeared to be the best
classifier.
Provided hyper-parameters are properly tuned, the superiority of
tree-based methods is in our opinion not surprising.
Indeed, given the fact that the optimal linkage function is likely to be non-linear, non-parametric
methods are expected to yield better results, as the experiments here confirm.

@@

@@

Using Recursive Feature Elimination \cite{guyon2002gene}, we next evaluate the
usefulness of all fifteen standard and seven additional ethnicity features for learning
the linkage function. The analysis consists in using the baseline algorithm
first using all twenty two features, to determine the least discriminative from feature
importances \cite{louppe2013understanding}, and then re-learn the baseline
using all but that one feature. That process is repeated recursively until
eventually only one feature remains. Results are presented in
Figure~\ref{fig:rfe} for one of the three folds, starting from the far right with
the baseline and \textit{Second given name} being the least important feature,
and ending on the left with all features eliminated but \textit{Chinese}. As
the figure illustrates, the most important features are ethnic-based features
(\textit{Chinese}, \textit{Other Asian}, \textit{Black}) along with
\textit{Co-authors}, \textit{Affiliation} and \textit{Full name}. Adding the remaining
other features only brings marginal improvements, with \textit{Journal},
\textit{Abstract}, \textit{Collaborations}, \textit{References}, \textit{Given
name initial} and \textit{Second given name} being almost insignificant.
Overall, these results highlight the added value of the proposed ethnicity
features.
Their duality in modeling both the similarity between author names
and their origins make them very strong predictors for author disambiguation.
The results also corroborate those from \cite{kang2009co} or \cite{ferreira2010effective}, who
found that the similarity between co-authors was a highly discriminative
feature.
If computational complexity is a concern, this analysis also
shows how decent performance can be achieved using only a very
small set of features, as also observed in
\cite{treeratpituk2009disambiguating} or \cite{levin2012citation}.

\textit{Semi-supervised clustering.} The last part of our experiment concerns
the study of agglomerative clustering and the best way to find a cut-off
threshold to form clusters. Results from Table~\ref{table:results}
first clearly indicate that average linkage is significantly better than
both single and complete linkage.

Clustering together all signatures from the same block is the least effective
strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
fact it requires almost no computation (\ie, both learning a linkage function
and running agglomerative clustering can be skipped -- only the blocking
function is needed to group signatures). In particular, this result reveals
that author names are not ambiguous in most cases\footnote{This holds for the
data we extracted, but may in the future, with the rise of non-Western
researchers, be an underestimate of the ambiguous cases.} and that only a small
fraction of them requires advanced disambiguation procedures. On the other
hand, both global and block cut thresholding strategies give very good results,
with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
researcher at the beginning of his career), this therefore suggests that either using
a cut-off threshold learned globally from the known data or using SFI would in general give
satisfactory results, only marginally worse than if claimed signatures had been
known. Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.

\textit{Combined best settings.} When all best settings are combined (\ie, Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance reaches $0.9862$, \ie, the best of all reported results. In particular,
this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm
and the high precision of Random Forests.

\textit{Execution time.} Our implementation takes around $20$ hours to process the complete set of the data (for 10M signatures, on a $16$ cores machine with $32$GB of RAM). Related work \cite{khabsa2014large} reports execution times around $24$ hours to cluster $4$M signatures. Note also that shorter execution times can be achieved, at the expense of worse results.

>>>>

Formally, let us assume a set of publications \\ ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (\eg, the author name, his
affiliation, along with any other metadata that can be derived from $p$, as illustrated in Figure~\ref{fig:signature}). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$.

@@

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
or study.
Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \cite{scikitlearn} for the supervised learning
of a linkage function and of SciPy \cite{scipy} for clustering.
All components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \cite{scikitlearnAPI}, making them easy to maintain,
understand and reuse.
Our implementation is made to be efficient, exploiting parallelization when available, and ready for production environments.
It is also designed to be runnable in an incremental fashion in which our approach is considered to be scalable. We adopt a divide-and-conquer strategy for clustering (called “blocking” in this line of work) in order to reduce the computational complexity from $O(N^2)$ to $O(\sum N_i^2)$, which in practice tends to ${O(N)}$ when $N_i << N$. This also means that instead of having to run the disambiguation process on the whole signature set, the process could be run only on specified blocks if desired.

@@

\begin{table*}
\caption{Average precision, recall and f-measure scores on test folds.}
\label{table:results}
\centering
\begin{tabular}{|l|c c c | c c c|}
  \hline
                       & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}}\\
  \textbf{Description} & $P$ & $R$ & $F$ & $P$ & $R$ & $F$ \\
  \hline
  \hline
Baseline & 0.9024 & 0.9828 & 0.9409  & 0.8298 & 0.9776 & 0.8977 \\
\hline
\underline{Blocking = SFI} & 0.9901 & 0.9760 & 0.9830  & 0.9948 & 0.9738 & 0.9842\\
Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841  & 0.9927 & 0.9817 & 0.9871 \\
Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850}  & 0.9936 & 0.9814 & \textbf{0.9875} \\
Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
\hline
No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
\underline{Name normalization} & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842}  \\
\hline
\hline
\underline{Classifier = GBRT} & 0.9901 & 0.9760 & 0.9830   & 0.9948 & 0.9738 & 0.9842 \\
Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846}  & 0.9957 & 0.9752 & \textbf{0.9854} \\
Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666 & 0.9717 & 0.9569 & 0.9643 \\
\hline
Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711  & 0.9756 & 0.9629 & 0.9692 \\
Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786  & 0.9850 & 0.9707 & 0.9778 \\
\underline{Training pairs = Blocked, balanced} & 0.9901 & 0.9760 & \textbf{0.9830}  & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
\hline
\underline{Clustering = Average linkage} & 0.9901 & 0.9760 & \textbf{0.9830}  & 0.9948 & 0.9738 & \textbf{0.9842} \\
Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671  & 0.9543 & 0.9626 & 0.9584 \\
Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785  & 0.9920 & 0.9688 & 0.9803 \\
\hline
No cut (baseline) & 0.9024 & 0.9828 & 0.9409  & 0.8298 & 0.9776 & 0.8977 \\
Global cut & 0.9892 & 0.9737 & 0.9814  & 0.9940 & 0.9727 & 0.9832 \\
\underline{Block cut} & 0.9901 & 0.9760 & \textbf{0.9830}  & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
\hline
Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862}  & 0.9954 & 0.9805 & \textbf{0.9879} \\
  \hline
\end{tabular}
\end{table*}

Our approach could be considered as an experimental design solution. Our goal is to find the best combination of design parameters. Such a solution could be reached by performing many experiments where in each experiment we fix all design parameters except one. Of course, what we found as a best choice in each experiment will be used for the proceeding one and so on. To initialize the process, we will use what have been reported by some related works as a best method.

\textit{state-of-the-art.} Unfortunately, most methods proposed in related works have released neither their software, nor their data, making in practice a fair comparison very difficult. However, we believe state-of-the-art algorithms proposed in the literature could still be shown by categorizing the design parameters into the three categories; blocking strategy, linkage function, and clustering and compare the choices per each category. This categorization represents the three main phases in the pipeline. We believe that results for different settings somehow reflects some of these state-of-the-art choices as we will show in this section. Results presented in Table ~\ref{table:results} are discussed with
respect to a state-of-the-art using the following parameter design setting per category. In Table ~\ref{table:results}, what we considered as state-of-the-art choice is underlined which are as follows:

\begin{itemize}
	\item Blocking: same surname and the same first given name initial strategy (SFI) and with name normalization;
	\item Linkage function: all 22 features defined in Table~\ref{table:features},
	gradient boosted regression trees as supervised learning algorithm
	and a training set of pairs built from $({\cal S}_\text{train}^\prime, {\cal C}_\text{train}^\prime)$, by balancing easy and difficult cases.
	\item Clustering: agglomerative clustering using average linkage and
	block cuts found to maximize \\ $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
\end{itemize}

\textit{Baseline.} Using machine learning techniques should perform better than dealing with the problem with other simpler method. Accordingly, we have set our experiment baseline having neither linkage function nor clustering. Actually, This is the case of many digital library where they use a simple and very fast execution solution with acceptable performance. Accordingly, our baseline algorithm is simply to group the set of publications from author names that have common surname and first initial as denoted in section \ref{methods:blocking} by \textit{SFI} and label them with a distinct author. However, this baseline also considers \textit{Name Normalization} for the 5 cases that is also previously discussed in section \ref{methods:blocking}. The results of the baseline is reported in the top of  Table ~\ref{table:results}.

In sections \ref{choices:blocking}, \ref{choices:linkage}, and \ref{choices:clustering}, we will discuss each group of design parameters in respect to the state-of-the-art choice of that group. Keep in mind that the results of each group uses the best of the other design parameters.

\subsubsection{Blocking choices} 
\label{choices:blocking}
The good precision of the state-of-the-art ($0.9901$), but its
lower recall ($0.9760$) suggest that the blocking strategy might be the
limiting factor to further overall improvements.
As shown in Table~\ref{table:blocking}, the maximum recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
At the price of fewer and therefore slightly larger blocks (as reported in the right column of Table~\ref{table:blocking}), the
proposed phonetic-based blocking strategies show better maximum recall (all
around $0.9905$), thereby pushing further the upper bound on the maximum
performance of author disambiguation.
Let us remind however that the reported maximum recalls for the blocking strategies using phonetization are
also raised due to the better handling of multiple surnames, as described in Section \ref{methods:blocking}.

As Table~\ref{table:results} shows, switching to either Double metaphone or NYSIIS phonetic-based blocking allows
to improve the overall F-measure score, trading precision for recall.
In particular, the NYSIIS-based phonetic blocking shows to be the most effective when applied
to the state-of-the-art (with an F-measure of $0.9850$) while also being the most
efficient computationally (with 10857 blocks versus 12978 for the baseline).

@@

\textit{Name normalization.} As discussed previously, the seemingly insignificant step of
normalizing author names (stripping accents, removing affixes), as performed in the
state-of-the-art, is shown to be important. Results from Table~\ref{table:results} clearly suggest that not
normalizing significantly reduces performance (yielding an F-measure of $0.9830$ when normalizing,
but decreasing to $0.9791$ when raw author name strings are used instead).

\subsubsection{Linkage function choices} 
\label{choices:linkage}
Let us first comment on the results regarding the
supervised algorithm used to learn the linkage function.
As Table~\ref{table:results} indicates, both tree-based algorithms appear to be
significantly better fit than Linear Regression ($0.9830$ and $0.9846$ for GBRT
and Random Forests versus $0.9666$ for Linear Regression). This result is
consistent with \cite{treeratpituk2009disambiguating} which evaluated the use of
Random Forests for author disambiguation, but contradicts results of
\cite{levin2012citation} for which Logistic Regression appeared to be the best
classifier.
Provided hyper-parameters are properly tuned, the superiority of
tree-based methods is in our opinion not surprising.
Indeed, given the fact that the optimal linkage function is likely to be non-linear, non-parametric
methods are expected to yield better results, as the experiments here confirm.

@@

Using Recursive Feature Elimination \cite{guyon2002gene}, we next evaluate the
usefulness of all fifteen standard and seven additional ethnicity features for learning
the linkage function. The analysis consists in using the state-of-the-art algorithm
first using all twenty two features, to determine the least discriminative from feature
importances \cite{louppe2013understanding}, and then re-learn the state-of-the-art algorithm
using all but that one feature. That process is repeated recursively until
eventually only one feature remains. Results are presented in
Figure~\ref{fig:rfe} for one of the three folds with
the state-of-the-art, starting from the far right, \textit{Second given name} being the least important feature,
and ending on the left with all features eliminated but \textit{Chinese}. As
the figure illustrates, the most important features are ethnic-based features
(\textit{Chinese}, \textit{Other Asian}, \textit{Black}) along with
\textit{Co-authors}, \textit{Affiliation} and \textit{Full name}. Adding the remaining
other features only brings marginal improvements, with \textit{Journal},
\textit{Abstract}, \textit{Collaborations}, \textit{References}, \textit{Given
name initial} and \textit{Second given name} being almost insignificant.
Overall, these results highlight the added value of the proposed ethnicity
features.
Their duality in modeling both the similarity between author names
and their origins make them very strong predictors for author disambiguation.
The results also corroborate those from \cite{kang2009co} or \cite{ferreira2010effective}, who
found that the similarity between co-authors was a highly discriminative
feature.
If computational complexity is a concern, this analysis also
shows how decent performance can be achieved using only a very
small set of features, as also observed in
\cite{treeratpituk2009disambiguating} or \cite{levin2012citation}.

@@

\subsubsection{Semi-supervised clustering choices}  
\label{choices:clustering}
The last part of our experiment concerns
the study of agglomerative clustering and the best way to find a cut-off
threshold to form clusters. Results from Table~\ref{table:results}
first clearly indicate that average linkage is significantly better than
both single and complete linkage.

Clustering together all signatures from the same block (\ie, baseline) is the least effective
strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
fact it requires almost no computation (\ie, both learning a linkage function
and running agglomerative clustering can be skipped -- only the blocking
function is needed to group signatures). In particular, this result reveals
that author names are not ambiguous in most cases\footnote{This holds for the
data we extracted, but may in the future, with the rise of non-Western
researchers, be an underestimate of the ambiguous cases.} and that only a small
fraction of them requires advanced disambiguation procedures. On the other
hand, both global and block cut thresholding strategies give very good results,
with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
researcher at the beginning of his career), this therefore suggests that either using
a cut-off threshold learned globally from the known data or using SFI would in general give
satisfactory results, only marginally worse than if claimed signatures had been
known. Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.

\subsubsection{Combined best settings} When all best settings are combined (\ie, Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance reaches $0.9862$, \ie, the best of all reported results. In particular,
this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm
and the high precision of Random Forests.

\subsubsection{Execution time} Our implementation takes around $20$ hours to process the complete set of the data (for 10M signatures, on a $16$ cores machine with $32$GB of RAM). Related work \cite{khabsa2014large} reports execution times around $24$ hours to cluster $4$M signatures. Note also that shorter execution times can be achieved, at the expense of worse results.
